\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\begin{document}
\header{claudio}{alessi}{1984-11-14}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Via H. C. Andersen, 10
90146 Palermo (PA)
Italy
~
\href{mailto:smoppy@gmail.com}{smoppy@gmail.com}
\section{languages}
italian mother tongue
english good
\section{programming}
C, CSS3 \& HTML5,
JavaScript, PHP, Python, unix shell
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{education}
\begin{entrylist}
%------------------------------------------------
\entry
{2002--2004}
{Diploma {\normalfont of Business Administration}}
{Ludovico Ariosto Institute}
{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{experience}
\begin{entrylist}
%------------------------------------------------
\entry
{2015--current}
{Pixelo s.r.l.}
{Palermo, Italy}
{\emph{Software developer} \\
I mantain and extend an online betting platform for our customers inside a big
developers team. I also design and implement cross-platform mobile apps.

I learned C\# to contribute on our server-side code and significantly improved
my understanding of JavaScrpt while working on our large codebase. Finally, I
learned React Native which I proeficiently use to develop mobile apps.
}
%------------------------------------------------
\entry
{2013--2015}
{Wiralist}
{Palermo, Italy}
{\emph{Lead developer} \\
Designed and developed a social network. We used MySQL to store data and redis for cache. This has been my first experience with the Laravel framework. \\
Details:
\begin{itemize}
\item Learned how to use the Laravel framework
\item Built a custom framework born from newly learned concepts
\item Configured and mantained cloud-based servers and services
\end{itemize}

Responsive web site where I used the following technologies: HTML,
JavaScript, AJAX, jQuery (plugins: fancybox, fileUpload), jQuery UI,
CSS (bootstrap, normalize.css), fontello.
}
%------------------------------------------------
\entry
{2010--2013}
{Pubblicarrello.com}
{Palermo, Italy}
{\emph{Lead developer} \\
Designed and developed an e-commerce with plenty of automations. Rated "truly distinctive"
for Conceptualizing, Problem Solving skills and Teamwork.

In this work I used the following technologies: HTML,
JavaScript, AJAX, jQuery (plugin: fancybox, tooltipster, fileUpload),
jQuery UI, CSS (reset.css), fontello.
}
%------------------------------------------------
\entry
{2009-2010}
{Learning Academy}
{Palermo, Italy}
{\emph{Professor in Computer Science} \\
Course in advanced understanding of Unix-like operating systems, like GNU/Linux.
}
%------------------------------------------------
\entry
{2007-2009}
{Freelance}
{Palermo, Italy}
{\emph{Freelancer} \\
Web developer, analyst, system administrator, technical assistance and consulting
}
%------------------------------------------------
\entry
{2006-2007}
{Civil Service}
{Palermo, Italy}
{\emph{Credited to the Civil Service} \\
IT Manager
}
%------------------------------------------------
\entry
{2005-2006}
{Achtiva s.r.l.}
{Palermo, Italy}
{\emph{IT Manager and Web master}
}
%------------------------------------------------
\entry
{2004-2005}
{Mac\&Win s.r.l.}
{Palermo, Italy}
{\emph{Technical Manager} \\
Tech support, customer relations and repair workshop.
}
%------------------------------------------------
\entry
{2001-2004}
{Freelance}
{Palermo, Italy}
{\emph{Freelancer} \\
Design and implementation of web sites, technical support, SEO.
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
\section{interests}
\textbf{professional:} web app creation, data analysis, design, software design, marketing
\textbf{personal:} piano, cooking, trading.

\end{document}
